---
title: "Hello R"
author: "Lauren Duvall"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 142 rows and 26 variables (columns). The variables include away_x, away_y, bullseye_x, bullseye_y, circle_x, circle_y, dino_x, dino_y, dots_x, dots_y, h_lines_x, h_lines_y, high_lines_x, high_lines_y, slant_down_x, slant_down_y, slant_up_x, slant_up_y, star_x, star_y, v_lines_x, v_lines_y, wide_lines_x, wide_lines_y, x_shape_x, x_shape_y. 

datasaurus_dozen %>%
count(dataset) %>%
print(13)

## # A tibble:
## #  13 x 2
##   dataset
##   <chr>
##  1 away
##  2 bullseye
##  3 circle 
##  4 dino
##  5 dots 
##  6 h_lines
##  7 high_lines
##  8 slant_down
##  9 slant_up
## 10 star
## 11 v_lines
## 12 wide_lines
## 13 x_shape
## # ... with 1
## #   more
## #   variable 
## #   n <int>


### Exercise 2

Plot y vs. x for the dino dataset. 

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset: -0.06447185

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
## # A tibble: 1 x 1
##       r
##   <dbl>
## 1 -0.0645


### Exercise 3
 
 Plot y vs. x for the star dataset. 

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Calculate the coordination between x and y in this dataset: -0.0629611
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

## # A tibble: 1 x 1
##         r
##     <dbl>
## 1 -0.0645

When comparing the correlation coefficient between the dino and star datasets, they are very close but star is slightly smaller.  
 
### Exercise 4

Plot y vs. x for the circle dataset. 

```{r cor-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Calculate the coordination between x and y in this dataset: -0.06834336

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

```
When comparing the correlation coefficient between the dino and circle datasets, they are very close but circle is slightly smaller. 


### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
```{r}

```

